\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\rhead{Abstract}

Protein-protein interaction networks are very important graph models which can reveal the relationship between proteins in a species. One can get much knowledge about proteins of the species by analyzing the PPI networks. Through the alignment of PPI networks, biological knowledge can be transferred between different species. Therefore, the goodness of the network alignment algorithms is very important.

On the other side, with much gene expression data, the concept of dynamic PPI networks is proposed which is obviously a new challenge to state-of-the-art static network alignment algorithms. The new concepts of alignment and alignment quality measurement, need to be defined when the condition changes from static PPI networks to dynamic ones.

This paper proposes the concept of alignment of dynamic PPI networks, defines the measurements of alignment quality, and designed an algorithm called SGOPT(SeGment OPTimization) which can be used to improve any alignment results produced by state-of-the-art static alignment algorithms. SGOPT maintains alignment by adjusting alignment locally and through a data structure called segment tree in environment of dynamic PPI networks. SGOPT finally can produce better alignments then state-of-the-art ones which is proved through systematic experiments in this paper.
\bigskip
\bigskip

\noindent{\bf Keywords}: protein-protein interaction networks, algorithms of alignment of PPI networks, dynamic PPI networks, segment tree, SGOPT